Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-25 VMCAI-revised-version/final.tex
up

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$, a control state $q_f \in Q$.}
{ $Q \times \longrightarrow^{*} q_f({\bf 0})$ ? \\}

>>>>

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$, a control state $q_f \in Q$.}
{ $Q \times \N^d \longrightarrow^{*} q_f({\bf 0})$ ? \\}
